Sequential Composition for Relaxed Memory: Pomsets with Predicate Transformers

### 2021-07-08 paper/tool.tex
Comment out tool screenshot & reference sentence Not enough space D:

\PwTer{} allows several modes of evaluation: it can evaluate the rules of Fig.~\ref{fig:seq}, implementing \PwT; it can generate program order according to \textsection\ref{sec:c11}, implementing \PwTpo; and similar to \MRD~\cite{DBLP:conf/esop/PaviottiCPWOB20}, it can construct C11-style pre-executions and filter them according to the rules of \rcXI{} as described in \textsection\ref{sec:c11}.
Finally, \PwTer{} also allows us to toggle the complete check of~\ref{def:complete}, providing an interface for understanding how fragments of code might compose by exposing preconditions and termination conditions that are not yet tautologies.
We show \PwTer{} in action in Fig.~\ref{fig:tool}. 
\PwTer{} will be made open source upon publication.
%\PwTer{} is available online at \url{https://github.com/graymalkin/pomsets-with-predicate-transformers}.

%% TODO: introduce some nice dogma about the value of a tool and what it's taught us.
%% The real friends are the tools we built along the way.

%% Notes for Simon and Mark:
% Intro
%  - Add contribution relating to tool

% Related work
%  - Mention tool for MRD & Event Structures, mention absence of tool for Promising

% This section
%  - tool for {PwT, PwT-PO, PwT-RC11}
%  - Validation of some tests? Which tests to include?

% C11 Section
%  - Discussion: C11 standard really needs a dep relation. MRD provides this, PwT provides this, Promising does not.
%  - There's an open question about how coherence should affect dep.
%    if(q) { x := 1; x := 2 } else { x := 2; x := 1 }
%  - What should the deps be?

% Conclusion
%  - Having a tool should be some kind of feel-good factor.

%% [Simon] I am not a fan of how this looks on the page.
\begin{figure}[t]
\begin{center}
  \includegraphics[width=0.75\textwidth]{tool.png}
  \Description{Image shows tool running on a Mac. Java Causality Test Case 1 is printed, followed by an invocation of the tool as {\tt ./pomsets.exe --check --complete data/tests/jctc/jctc1.lit}, which shows that the tool passes the assertion listed in the test.}
  \caption{\label{fig:tool} Example output of \PwTer, validating TC1~\cite{PughWebsite}.}
\end{center}
\end{figure}

>>>>

\PwTer{} allows several modes of evaluation: it can evaluate the rules of Fig.~\ref{fig:seq}, implementing \PwT; it can generate program order according to \textsection\ref{sec:c11}, implementing \PwTpo; and similar to \MRD~\cite{DBLP:conf/esop/PaviottiCPWOB20}, it can construct C11-style pre-executions and filter them according to the rules of \rcXI{} as described in \textsection\ref{sec:c11}.
Finally, \PwTer{} also allows us to toggle the complete check of~\ref{def:complete}, providing an interface for understanding how fragments of code might compose by exposing preconditions and termination conditions that are not yet tautologies.
% We show \PwTer{} in action in Fig.~\ref{fig:tool}. 
\PwTer{} will be made open source upon publication.
%\PwTer{} is available online at \url{https://github.com/graymalkin/pomsets-with-predicate-transformers}.

%% [Simon] I am not a fan of how this looks on the page.
% \begin{figure}[t]
% \begin{center}
%   \includegraphics[width=0.75\textwidth]{tool.png}
%   \Description{Image shows tool running on a Mac. Java Causality Test Case 1 is printed, followed by an invocation of the tool as {\tt ./pomsets.exe --check --complete data/tests/jctc/jctc1.lit}, which shows that the tool passes the assertion listed in the test.}
%   \caption{\label{fig:tool} Example output of \PwTer, validating TC1~\cite{PughWebsite}.}
% \end{center}
% \end{figure}
